beautier: BEAUti for R

### 2017-12-20 article.tex
First go

\usepackage{listings}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{pgf}
\usetikzlibrary{arrows,automata}

@@

@@

\verb;beautier; successfully creates valid BEAST2 input files. Unlike BEAUti,
\verb;beautier; allows for setting a fixed crown age.

\verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
for that the \verb;RBeast; package is recommended.

The package is free and is available from the official R package archive at 
http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier. 
\verb;beautier; is licensed under the GNU General Public License.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We would like to thank the Center for Information Technology of the University of Groningen for their support
and for providing access to the Peregrine high performance computing cluster.

>>>>

\usepackage{listings}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{pgf}
\usetikzlibrary{arrows,automata}

@@

\verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
for that the \verb;RBeast; \cite{RBeast} package is recommended.

@@

\verb;beautier; is free, libre and open source software available from the official R package archive at 
\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier}.  
\verb;beautier; is licensed under the GNU General Public License.

\verb;beautier;'s development takes place on GitHub \cite{github}. 
GitHub is a website that hosts (among others) software and facilites its development.
Using GitHub is a good practice for computational scientists \cite{perez2016ten} 
and improves transparency \cite{gorgolewski2016practical}.

\verb;beautier;'s quality is assured by Travis CI \cite{travis}. Travis CI is
a continuous integration service, that runs a script upon a (suggested)
change in \verb;beautier;'s code. The \verb;beautier; script checks if the
package can be build, runs all unit and intergration tests, 
measures code coverage, coding style and good practices.

Unit and integration tests check the intergrity of \verb;beatier;. All functions
are tested for producing the correct output and desired error handling. 
Travis CI uses the testing facilities of the \verb;testthat; \cite{testthat} package.

Code coverage is the percentage of code that is executed in tests. 
Code coverage correlates with code quality \cite{del1995correlation}. 
Travis CI uses the \verb;covr; \cite{covr} package to measure code coverage. 
\verb;beautier; has a 100\% code coverage.

Coding style is the way statements are laid out, for example the placement of 
curly brackets. \verb;beautier; follows Hadley Wickham's style guide. 
Travis CI uses the \verb;lintr; \cite{lintr} package to comfirm this coding style
is used.

Good practices are miscellaneous things considered good practices. An example
of a good practice is (next to high code coverage and consistent coding style) 
to have short functions with a low cyclomatic complexity. Travis CI uses 
the \verb;goodpractice; \cite{goodpractice} package to comfirm all good practices
are followed.

\verb;beautier; is dependent on multiple packages, which are 
\verb;APE; \cite{APE}, 
\verb;devtools; \cite{devtools},
\verb;geiger; \cite{GEIGER},
\verb;ggplot2; \cite{ggplot2},
\verb;knitr; \cite{knitr},
\verb;phangorn; \cite{phangorn},
\verb;RBeast; \cite{RBeast},
\verb;rmarkdown; \cite{rmarkdown},
\verb;seqinr; \cite{seqinr},
\verb;stringr; \cite{stringr},
\verb;testit; \cite{testit} and 
\verb;TreeSim; \cite{TreeSim}.

\verb;beautier;'s documentation is extensive, yet concise. All funnctions are documented
in the package's internal documentation. For quick use, each exported function shows a minimal example. 
For easy exploration, each exported function's documentation links to related functions.
Additionally, \verb;beautier; has a vignette that demonstrates in a longer form how
to use it. The integrity of this documentation is tested each time the package is built by Travis CI.
The documentation on the GitHub helps to get started, with a dozen examples 
of a BEAUti screenshot and the equivalent \verb;beautier; code.

\verb;beautier;'s GitHub facilitates feature requests and guidelines how to do so.
New code can be submitted using GitHub's infrastructure (a 'Pull Request'). New
code will be tested by Travis CI to follow the same quality standards and only accepted
when there are no

@@
